Viscous Transport in Eroding Porous Media

### 2019-09-05 docs/transport/erosion_transport.tex
working on 100 body example

The tortuosity at all porosities from the initial condition until all
the bodies have eroded is in Figure~\ref{fig:Eroding100tort_all}.  The
initial tortuosity is around $T=1.2$ and decays towards $T=1$.  The
tortuosities indicated by the blue dots are calculated using the
Eulerian approach~\eqref{eqn:tortuosity2}, while the red marks use the
Lagrangian approach~\eqref{eqn:tortuosity1}.  Again, the two methods
give comparable results indicating that any recirculation is small and
negligible.  As in the previous examples, the tortuosity depends on the
porosity through a power law model with a small root-mean-squared error
of $5.2 \times 10^{-3}$.  For this example, the logarithm tortuosity
model $\hat{T}(\phi) = 1 - p \ln(\phi)$ achieves a similar
root-mean-squared error.  The tortuosity has one interesting feature
near the end of the simulation where it suddenly increases.  This
behavior can be explained by ... \todo[inline]{S-H: Show me what is
going on here as we discussed.}

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/tort_eulerian100}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height=0.8\linewidth]{./figs/100b_second_moment_long_ref}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100Transport} (a): The tortuosity of an
eroding geometry initialized with 20 bodies.  When compared to the last
example, the bodies are initially much closer together, and the porosity
is smaller.  The tortuosity is calculated using the Eulerian
method~\eqref{eqn:tortuosity2} (blue dots).  The dash line is the
fitting line $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.1669$, and the root
mean square deviation is $1.13 \times 10^{-2}$.  (b): The temporal
evolution of $\sigma_\lambda$ as a function of time at eight different
porosities.  The dashed line, which has slope one, corresponds to the
ballistic dispersion $\sigma_\lambda \sim t$ if no bodies were present.
At early times, the particles undergo a ballistic motion, but once they
have traversed a few grains, the dispersion becomes super-dispersive
with $\sigma_\lambda \sim t^{\alpha}$, $\alpha \in (1/2,1)$.  The
dashed-dotted lines are lines of best fit with slope $0.92$
($\phi=95.00\%$), $0.87$ ($\phi=85.17\%$), $0.87$ ($\phi=75.10\%$),
$0.91$ ($\phi=65.02\%$), $0.91$ ($\phi=55.08\%$), $0.72$
($\phi=45.03\%$), $0.69$ ($\phi=35.05\%$), and $0.92$ ($\phi=30.67\%$).}
\caption[inline]{Fix this caption}
\end{figure}

\begin{figure}[H]
\center
\includegraphics*[width =0.55\linewidth]{./figs/tort_eulerian100}
\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian
approach of tortuosity.  The blue dots are Eulerian approach of
tortuosity and the red stars and square are Lagrangian approach of
tortuosity.  The dash line is the fitting line
$\widehat{T}(\phi)=\phi^{-p}$ as $p=0.2459$ and the root-mean-square
error is $5.5 \times 10^{-3}$.  We note that the model
$\widehat{T}(\phi) = 1-p\ln(\phi)$, with $p=0.2631$ has a comparable
root-mean-square error of $5.2 \times 10^{-3}$.}
\end{figure}

Next, we use the 1000 tracer trajectories to compute the second
(Figure~\ref{fig:Eroding100anomalous}) moments of the streamlines at
various porosities.  At high porosities, the first moment is similar to
the first-moment of trajectories in a empty channel (black dashed line).
At smaller porosities, the first moment is always linear, but larger
slopes indicate that the length of the trajectories are longer at lower
porosities \todo[inline]{Don't understand how this is the case}.  The
onset of anomalous dispersion is observed in
Figure~\ref{fig:Eroding100anomalous}. At early times, the particle
spreading is comparable to that of an open channel (dashed curve)
corresponding to the ballistic regime.  However, as the trajectories
traverse the geometry, a transition to a super-dispersive case,
especially at low porosities, is evident.  The dashed-dotted line
corresponds has a slope less than 1 indicating the long time behavior of
the trajectories
\begin{align*}
  \sigma_\lambda \sim t^{0.8715}.
\end{align*}

\begin{figure}
\center
\includegraphics*[width =0.55\linewidth]{./figs/100b_second_moment_long_ref}
\caption{\label{fig:Eroding100anomalous} The analysis of anomalous
dispersion in 100 bodies with respect to initial porosity
(as p=50.09\%) and another five porosities during the eroding. The dashed line
correspondes to a porosity of 100\% and the dashed-dotted lines are lines
of best fit with slope 1.1135 (as p=95.12\%), 0.6825 (as p=85.07\%), 
0.7347 (as p=75.14\%), 0.5915 (as p=65.03\%), 
0.6107 (as p=55.02\%), and 0.7 (as p=50.09\%).}
\end{figure}

@@

%\begin{figure}[H]
%\center
%\includegraphics*[width =0.55\linewidth]{./figs/tort_eulerian20b}
%\caption{\label{fig:ErodingLow20tort} The tortuosity inside of an
%eroding geometry initialized with 20 bodies.  The tortuosity is
%calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue
%dots).  The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$
%as $p=0.1669$ and the root mean square deviation is $1.13 \times
%10^{-2}$.}
%\end{figure}
%
%\begin{figure}[H]
%\center
%\includegraphics*[width =0.55\linewidth]{./figs/20b_dense_second_moment_ref}
%\caption{\label{fig:Eroding20anomalousLow} The analysis of anomalous
%dispersion in 20 nearly touching bodies with respect to initial porosity
%(as p=30.67\%) and another seven porosities during the eroding. The
%dashed line correspondes to a porosity of 100\% and the dashed-dotted
%lines are lines of best fit with slope 0.9194 (as p=95\%), 0.8666 (as
%p=85.17\%), 0.8682 (as p=75.10\%), 0.9087 (as p=65.02\%), 0.9054 (as
%p=55.08\%), 0.7234 (as p=45.03\%), 0.6895 (as p=35.05\%), and 0.9225 (as
%p=30.67\%).}
%\end{figure}

>>>>

The tortuosity at all porosities from the initial condition until all
the bodies have eroded is in Figure~\ref{fig:Eroding100Transport}(a).
The initial tortuosity is around $T=1.2$ and decays towards $T=1$.  The
tortuosities indicated by the blue dots are calculated using the
Eulerian approach~\eqref{eqn:tortuosity2}, while the red marks use the
Lagrangian approach~\eqref{eqn:tortuosity1}.  Again, the two methods
give comparable results indicating that any recirculation is small and
negligible.  As in the previous examples, the tortuosity depends on the
porosity through a power law model with a small root-mean-squared error
of $5.2 \times 10^{-3}$.  For this example, the logarithm tortuosity
model $\hat{T}(\phi) = 1 - p \ln(\phi)$ achieves a similar
root-mean-squared error.  The tortuosity has one interesting feature
near the end of the simulation where it suddenly increases.  This
behavior can be explained by ... \todo[inline]{S-H: Show me what is
going on here as we discussed.}

Next, we use the 1000 tracer trajectories to compute the second
(Figure~\ref{fig:Eroding100Transport}(b)) moments of the streamlines at
various porosities.  At high porosities, the first moment is similar to
the first-moment of trajectories in a empty channel (black dashed line).
At smaller porosities, the first moment is always linear, but larger
slopes indicate that the length of the trajectories are longer at lower
porosities \todo[inline]{Don't understand how this is the case}.  The
onset of anomalous dispersion is observed in
Figure~\ref{fig:Eroding100anomalous}. At early times, the particle
spreading is comparable to that of an open channel (dashed curve)
corresponding to the ballistic regime.  However, as the trajectories
traverse the geometry, a transition to a super-dispersive case,
especially at low porosities, is evident.  The dashed-dotted line
corresponds has a slope less than 1 indicating the long time behavior of
the trajectories
\begin{align*}
  \sigma_\lambda \sim t^{0.8715}.
\end{align*}

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.8\linewidth]{./figs/tort_eulerian100}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height=0.8\linewidth]{./figs/100b_second_moment_long_ref}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100Transport} (a): The tortuosity of an
eroding geometry initialized with 100 bodies.  The tortuosity is calculated using the Eulerian
method~\eqref{eqn:tortuosity2} (blue dots).  The dash line is the
fitting line $\widehat{T}(\phi)=\phi^{-p}$ with $p=0.2459$, and the root
mean square deviation is $5.50 \times 10^{-3}$.  We note that the model
$\widehat{T}(\phi) = 1 - p \ln (\phi)$, with $p=0.2631$ has a comparable
root-mean-square error of $5.20 \times 10^{-3}$.  (b): The temporal
evolution of $\sigma_\lambda$ as a function of time at six different
porosities.  The dashed line, which has slope one, corresponds to the
ballistic dispersion $\sigma_\lambda \sim t$ if no bodies were present.
At early times, the particles undergo a ballistic motion, but once they
have traversed a few grains, the dispersion becomes super-dispersive
with $\sigma_\lambda \sim t^{\alpha}$, $\alpha \in (1/2,1)$.  The
dashed-dotted lines are lines of best fit with slope $1.11$
($\phi=95.12\%$), $0.68$ ($\phi=85.07\%$), $0.73$ ($\phi=75.14\%$),
$0.59$ ($\phi=65.03\%$), $0.61$ ($\phi=55.02\%$), and $0.70$
($\phi=50.09\%$).}
\end{figure}

@@

%\begin{figure}[H]
%\center
%\includegraphics*[width =0.55\linewidth]{./figs/tort_eulerian20b}
%\caption{\label{fig:ErodingLow20tort} The tortuosity inside of an
%eroding geometry initialized with 20 bodies.  The tortuosity is
%calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue
%dots).  The dash line is the fitting line $\widehat{T}(\phi)=\phi^{-p}$
%as $p=0.1669$ and the root mean square deviation is $1.13 \times
%10^{-2}$.}
%\end{figure}
%
%\begin{figure}[H]
%\center
%\includegraphics*[width =0.55\linewidth]{./figs/20b_dense_second_moment_ref}
%\caption{\label{fig:Eroding20anomalousLow} The analysis of anomalous
%dispersion in 20 nearly touching bodies with respect to initial porosity
%(as p=30.67\%) and another seven porosities during the eroding. The
%dashed line correspondes to a porosity of 100\% and the dashed-dotted
%lines are lines of best fit with slope 0.9194 (as p=95\%), 0.8666 (as
%p=85.17\%), 0.8682 (as p=75.10\%), 0.9087 (as p=65.02\%), 0.9054 (as
%p=55.08\%), 0.7234 (as p=45.03\%), 0.6895 (as p=35.05\%), and 0.9225 (as
%p=30.67\%).}
%\end{figure}
%
%\begin{figure}[H]
%\center
%\includegraphics*[width =0.55\linewidth]{./figs/tort_eulerian100}
%\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian
%approach of tortuosity.  The blue dots are Eulerian approach of
%tortuosity and the red stars and square are Lagrangian approach of
%tortuosity.  The dash line is the fitting line
%$\widehat{T}(\phi)=\phi^{-p}$ as $p=0.2459$ and the root-mean-square
%error is $5.5 \times 10^{-3}$.  We note that the model
%$\widehat{T}(\phi) = 1-p\ln(\phi)$, with $p=0.2631$ has a comparable
%root-mean-square error of $5.2 \times 10^{-3}$.}
%\end{figure}
%
%\begin{figure}
%\center
%\includegraphics*[width =0.55\linewidth]{./figs/100b_second_moment_long_ref}
%\caption{\label{fig:Eroding100anomalous} The analysis of anomalous
%dispersion in 100 bodies with respect to initial porosity
%(as p=50.09\%) and another five porosities during the eroding. The dashed line
%correspondes to a porosity of 100\% and the dashed-dotted lines are lines
%of best fit with slope 1.1135 (as p=95.12\%), 0.6825 (as p=85.07\%), 
%0.7347 (as p=75.14\%), 0.5915 (as p=65.03\%), 
%0.6107 (as p=55.02\%), and 0.7 (as p=50.09\%).}
%\end{figure}
